\chapter*{Attachment 4 : Native Agent Arguments}
The native agent accepts several arguments which can be used to affect the agent behavior. In the local instrumentation server mode, several arguments affect also the server started from the agent. Available arguments are:
\begin{itemize}
	\item \textbf{instrumentor\_server\_jar} - specifies the path to the instrumentation server JAR file. It is a mandatory argument in case the instrumentation server is supposed to run per each node of the monitored application.
	\item \textbf{instrumentor\_server\_cp} - specifies the classpath for the instrumentation server. It can be used to add application specific classes on the server classpath. This has the effect that the monitored application does not have to send these classes to the server if they need to be instrumented or if some class to be instrumented depends on them.
	\item \textbf{instrumentor\_main\_class} - specifies the main entry point for the instrumentation server. It is a required argument in the case of local instrumentation server mode.
	\item \textbf{connection\_str} - specifies the type of the connection between the native agent and the instrumentation server. It is a mandatory argument in shared instrumentation server mode in which case, the value is in format \texttt{tcp://ip:port}, where \texttt{ip:port} is the address of the instrumentation server. Otherwise, the agent and server communicates via inter-process communication and the argument can be set in format \texttt{ipc://identifier}, where the identifier specifies the name of a pipe in case of Windows and name of a file used for IPC in the case of Unix. However, this value is set automatically at run-time if not explicitly specified as the argument.
	\item \textbf{log\_dir} - specifies the log directory for the native agent. When running in the local server mode, specifies the log directory for the server as well.
	\item \textbf{log\_level} - specifies the log level for the native agent. When running in the local server mode, specifies the log level for the server as well.
	\item \textbf{span\_exporter} - specifies the span exporter type. The value can be either \linebreak \texttt{directZipkin(ip:port)}, where \texttt{ip:port} is the address of the Zipkin user interface or \texttt{disk(destination)}, where \texttt{destination} represents the output directory for the captured spans. 
	
	Custom span exporters are supported as well. In that case, the format of the value is fully qualified name of the span exporter with arguments in parenthesis, for example, as \texttt{com.span.exporter(arguments)}.
	\item \textbf{class\_output\_dir} - specifies the output directory for several helper classes received from the instrumentation server. This value is automatically set if not configured explicitly.
	\item \textbf{config\_file} - specifies the path to the configuration file containing the native agent configuration. It can contain all arguments mentioned above, except the configuration file argument. Argument entries in the configuration file are in the format \texttt{arg=value} and each entry is on a new line of the configuration file. 
\end{itemize}