\chapter*{Attachment 3: Building and Running the Distrace Tool}
To build both, the native agent and the core instrumentation server, the developer needs to obtain the Distrace tool sources\footnote{Distrace is available at \url{https://github.com/jakubhava/Distrace} or at the attached CD.} and call the \texttt{./gradlew build}\footnote{On Windows, the \texttt{gradlew.bat build} command.} command, which builds the tool and produces artifacts for the core instrumentation server and the native agent as well. 

The build process requires several dependencies to be available. The instrumentation server requires Java 8 to be available. It also depends on several libraries, but these are downloaded automatically by the build process. The native agent depends on several libraries, which need to be available on the system:
\begin{itemize}
	\item Boost-filesystem
	\item Boost-system
	\item Nanomsg
	\item Nanomsgxx
	\item Cmake
\end{itemize}
The last dependency is required for building the native agent project. The rest of the mentioned dependencies are used in the native agent code. Any C++11 compliant compiler needs to be available as well.

Once the artifacts are built, the developer may extend the core instrumentation server with the specification of custom instrumentation points. The final application with the monitoring enabled can be run using the following incantation:

\texttt{java -agentpath:"\$NATIVE\_AGENT\_LIB\_PATH=\$AGENT\_ARGS" -jar app.jar}

The \texttt{\$NATIVE\_AGENT\_LIB\_PATH} shell variable should point to the location of the native agent library and \texttt{\$AGENT\_ARGS} shell variable may contain any arguments passed to the native agent. The arguments are in the \texttt{key=value} format and are separated by the semicolon. Please see the Attachment 4 for the full list of available native agent arguments.

In order to be able to see the spans in the user interface, we need to start the Zipkin user interface first. The user interface server may be started as: \texttt{java -jar zipkin.jar}\footnote{The Zipkin Jar file may be downloaded from \url{https://github.com/openzipkin/zipkin} or is available at the attached CD.}.
\section*{Running Docker Examples}
 In order to run examples without the need to set up all dependencies, the Docker container with all examples is prepared. This container contains all Distrace dependencies and when started, is also automatically starts the Zipkin user interface on the default port. To run any example in Docker, Docker needs to be available, the Distrace source directory needs to be available\footnote{The Distrace sources are not actually needed for running the examples in Docker, but the script which is used to start the docker machine is located in this directory.} and the following script should be called: \texttt{./docker/run-test.sh}\footnote{On Windows, \texttt{docker/run-test.cmd}} inside the Distrace sources directory. This script expects a single argument representing the example name we want to start. When this argument is missing, the list of available examples is printed to the console.